CodeBook
========================================================

AcitivityRecogn.txt
---------------------------

AcitivityRecogn.txt contains a tidy dataset of **means** and **stds** of measurements extracted from **Human Activity Recognition Using Smartphones dataset**, which is available from **https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip**. More information of the original dataset can be found at **http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones**.

There are **10299** observations in total. The **1-7352th** observations are the training data, while the **7353-10299th** observations are the test data.

The dataset contains **68** variables. The **1-66th** variables are **means** and **stds** of measurements extracted from **x.train** and **x.test**. These are all **numeric** variables. 

The **67th** variable is the **subject** extracted from **subject.train** and **subject.test**, which is an **integer** variable. 

The **68th** variable is the **Activity** variable extracted from **y.train** and **y.test**. It is a **factor** variable with **6** levels.

The name of the variables are:

```{r,echo=FALSE}
type.name <- c("tBodyAcc-Mean","tBodyAcc-Std","tGravityAcc-Mean","tGravityAcc-Std","tBodyAccJerk-Mean","tBodyAccJerk-Std",
               "tBodyGyro-Mean","tBodyGyro-Std","tBodyGyroJerk-Mean","tBodyGyroJerk-Std")
type.name <- paste(rep(type.name, each=3), c("-X","-Y","-Z"), sep="")
temp <-c("tBodyAccMag","tGravityAccMag","tBodyAccJerkMag","tBodyGyroMag","tBodyGyroJerkMag")
temp <- paste(rep(temp, each=2), c("-Mean","-Std"), sep="")
type.name <- c(type.name, temp)
temp <- c("fBodyAcc","fBodyAccJerk","fBodyGyro")
temp <- paste(rep(temp, each=6), rep(c("-Mean","-Std"), each=3),sep="")
temp <- paste(temp, c("X","Y","Z"), sep="-")
type.name <- c(type.name, temp)
temp <- c("fBodyAccMag","fBodyBodyAccJerkMag","fBodyBodyGyroMag","fBodyBodyGyroJerkMag")
temp <- paste(rep(temp, each=2), c("-Mean","-Std"), sep="")
type.name <- c(type.name, temp,"Subject","Activity")
type.name
```

Note: when **AcitivityRecogn.txt** is loaded, the **-** in the variable names may become **.** due to system issue.

The levels of **Activity** is:

```{r,eval=FALSE}
1 WALKING
2 WALKING_UPSTAIRS
3 WALKING_DOWNSTAIRS
4 SITTING
5 STANDING
6 LAYING
```

The data can be loaded using the following command:

```{r,eval=FALSE}
mydata <- read.table("./AcitivityRecogn.txt", header=TRUE)
```


Avg_Of_AcitivityRecogn.txt
---------------------------

Avg_Of_AcitivityRecogn.txt contains a tidy dataset of **average** of **means** and **stds** of measurements extracted from **AcitivityRecogn dataset**.

There are **180** observations in total. Each observation corresponds to the average of each variable for each activity and each subject.

The dataset contains **68** variables. The **1-66th** variables are **average** of **means** and **stds** of measurements. These are all **numeric** variables. 

The **67th** variable is the **subject** varies from **1 to 30**, which is an **integer** variable. 

The **68th** variable is the **Activity** variable. It is a **factor** variable with **6** levels.

The name of the variables are:

```{r,echo=FALSE}
type.name <- c("tBodyAcc-Mean","tBodyAcc-Std","tGravityAcc-Mean","tGravityAcc-Std","tBodyAccJerk-Mean","tBodyAccJerk-Std",
               "tBodyGyro-Mean","tBodyGyro-Std","tBodyGyroJerk-Mean","tBodyGyroJerk-Std")
type.name <- paste(rep(type.name, each=3), c("-X","-Y","-Z"), sep="")
temp <-c("tBodyAccMag","tGravityAccMag","tBodyAccJerkMag","tBodyGyroMag","tBodyGyroJerkMag")
temp <- paste(rep(temp, each=2), c("-Mean","-Std"), sep="")
type.name <- c(type.name, temp)
temp <- c("fBodyAcc","fBodyAccJerk","fBodyGyro")
temp <- paste(rep(temp, each=6), rep(c("-Mean","-Std"), each=3),sep="")
temp <- paste(temp, c("X","Y","Z"), sep="-")
type.name <- c(type.name, temp)
temp <- c("fBodyAccMag","fBodyBodyAccJerkMag","fBodyBodyGyroMag","fBodyBodyGyroJerkMag")
temp <- paste(rep(temp, each=2), c("-Mean","-Std"), sep="")
type.name <- paste("Avg_Of_", type.name, sep="")
type.name <- c(type.name, temp,"Subject","Activity")
type.name
```

Note: when **Avg_Of_AcitivityRecogn.txt** is loaded, the **-** in the variable names may become **.** due to system issue. But the **_** will not.

The levels of **Activity** is:

```{r,eval=FALSE}
1 WALKING
2 WALKING_UPSTAIRS
3 WALKING_DOWNSTAIRS
4 SITTING
5 STANDING
6 LAYING
```

The data can be loaded using the following command:

```{r,eval=FALSE}
mydata <- read.table("./Avg_Of_AcitivityRecogn.txt", header=TRUE)
```